Lynott et al. (2014) - Potential error in statistics reporting

### 2017-11-09 manuscript.Rmd
Fixed caption for figure 1

```{r echo=FALSE, fig.width=5, fig.height=7, fig.cap=paste("put your figure caption here")}
#  Plot H0 and H1 regions for different significance tests
source("H0H1_plot.R")
```

Figure 1: Illustration of null hypotheses ($H_0$) and alternative hypotheses ($H_1$) for different types of significance tests. **A)** Equivalence test: Tests the hypothesis ($H_0$) that an effect is smaller than $\Delta_{L}$ *or* larger than $\Delta_{U}$. **B)** NHST: Tests the hypothesis ($H_0$) that an effect is equal to 0. **C)** Minimal effects test: Tests the hypothesis ($H_0$) that an effect is larger than $\Delta_{L}$ *and* smaller than $\Delta_{U}$. **D)** Inferiority test: Tests the hypothesis ($H_0$) that an effect is larger than $\Delta$.

>>>>

```{r echo=FALSE, fig.width=5, fig.height=7, fig.cap="Illustration of null hypotheses ($H_0$) and alternative hypotheses ($H_1$) for different types of significance tests. **A)** Equivalence test: Tests the hypothesis ($H_0$) that an effect is smaller than $\\Delta_{L}$ *or* larger than $\\Delta_{U}$. **B)** NHST: Tests the hypothesis ($H_0$) that an effect is equal to 0. **C)** Minimal effects test: Tests the hypothesis ($H_0$) that an effect is larger than $\\Delta_{L}$ *and* smaller than $\\Delta_{U}$. **D)** Inferiority test: Tests the hypothesis ($H_0$) that an effect is larger than $\\Delta$."}

#  Plot H0 and H1 regions for different significance tests
source("H0H1_plot.R")
```
